How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-01 tse-paper/content.tex
Extensive review until Section 3

\IEEEPARstart{I}{n}
the past two decades, Continuous Integration (CI) has become a
ubiquitous best practice to streamline the build process of software
projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
Build logs are a textual by-product that these automatic software
builds create.
As a treasure trove of information~\cite{meyer},
build logs contain trace outputs of not only the elementary steps to
``make'' a project---such as retrieving and resolving dependencies and
compiling---but also about ancillary quality assurance steps---such as
testing the software and running automated static analysis tools.
The
contents and format of build logs can vary highly depending on which tools
are involved in the build process, how they are
configured, and as projects and build tools evolve over
time~\cite{staahl2014modeling}.
Typically, though, they are at least a semi-structured and
somewhat stable journal of the commands executed during the build and
their results.

When a build or one of its steps fails, developers typically scavenge
the logs for information related to the source of the error.
This
manual activity is tedious and prone to
errors~\cite{santolucito2018statically}.
As a single build log can be
over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
of information which is linked to the actual error, is akin to
searching for a needle in a haystack.
The large numbers of unrelated, but ambiguous
warnings, which many build
logs regularly contain, further compound this problem.
In addition to helping
understand and fix build failures, the information richness of build
logs enables a plethora of other applications: with the help of build
logs, we can better understand and categorize CI failures and compile
errors~\cite{islam2017insights,seo2014programmers}, differentiate
testing practices~\cite{orellana2017differences,vassallo2017a-tale},
train classifiers to do ``predictive CI'' on the build or test outcome
and
duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,
machalica2019predictive},
or investigate the role of automated static analysis tools (ASATs)
in CI
builds~\cite{zampetti2017open}.

@@

Despite its central role in helping developers and in enabling
novel, onward processing applications,
the process of how to
%automatically
% ^ we survey manual as well, though leaving it out includes too much
systematically
analyze build logs has thus far not been systematically
overviewed as a research topic, bringing us to the first
research question:
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What is the state-of-research to analyze build logs?
\end{simplebox}

To answer this question, we start our investigation---pictured in
\Cref{fig:overview}---with an
extensive literature survey (step \circlenum{1}).
The survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
searching for keywords, or performing natural language processing.
However, there is currently no guidance on when to use which of these
approaches.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
the few available implementations are all based on either a custom parser
or regular expressions.
These two approaches are problematic, as their creation
and maintenance is manual and expensive, does not generalize across build
logs from different build tools, and is prone to errors,
as the experience of
TravisTorrent has
shown~\cite{beller2017travistorrent,travistorrentquestions}.
In fact, some even ``strongly discourage'' the creation of such
parsers~\cite{urli2018design}.
In summary, the outcome of our literature survey shows the need for a new
generation of automated techniques to analyze build logs, which are
openly available and documented in detail, together with
guidance on when to use which technique.

%Using 1) a set of
% manually curated regular expressions,
% similar to TravisTorrent~\cite{beller2017oops},
% 2) information
% retrieval techniques,
% % Can you shortly explain the technique here?
% and 3) a list of search keywords
% to identify regions of interest in the build log.

%% \begin{itemize}
%%   \item \textbf{(referred to as PBE)}
%%   Based on manually supplied example pairs of build logs and chunks,
%%   PBE automatically synthesizes
%%   a regular expression extracting the given chunks within the build
%% logs.
%%   % these second sentences about what the techniques stand for could
%%   % also be merged to a paragraph after the itemize
%%   PBE mimics regular expressions and parsers while
%%   simplifying their development.
%%   \item \textbf{Common Text Similarity (CTS)}
%%   Text similarity is a common information retrieval technique.
%%   CTS selects lines of a log which are
%%   most similar to the lines present in manually supplied example
%% chunks.
%%   As a common information retrieval technique, our text similarity
%%   approach stands for the machine learning approaches identified in
%%   the literature survey.
%%   \item \textbf{Keyword Search (KWS)}
%%   KWS finds fitting passages by searching the whole
%%   text of a build log for
%%   the occurrence of specific trigger words.
%%   Keyword Search was explicitly mentioned by several articles in the
%%   literature survey.
%% \end{itemize}

% turned into an itemize again cause the 'sentence' around it was
% rather broken and item-ish anyways
To fill this gap, we adapted and implemented three novel, prototypical
implementations to
automatically analyze build logs (step \circlenum{2}).
The ideas behind the implementations are based on promising approaches
adopted from other research fields and existing build log analysis
techniques.
In this article, we present three techniques that analyze a build log
by retrieving a substring (chunk):
\begin{itemize}
	\item \emph{Program Synthesis by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, using \emph{Common Text Similarity (CTS)}
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}
\end{itemize}
% a technique 1) able to automatically synthesize regular expressions,
% called \emph{Program Synthesis by Example (PBE)}, a technique
% 2) based on information
% retrieval, using \emph{Common Text Similarity (CTS)}	and 3)
% inspired by the manual ad hoc search for key parts in the log, a
% technique employing \emph{Keyword Search (KWS)}.
These three approaches---synthesized regular expressions,
text similarity, and
keyword search---have
different strengths and weaknesses.
As a consequence,
in the second research question we ask:

@@

To answer this question
we conduct an empirical study assessing the performance
of these chunk retrieval techniques in
real-world projects under a variety of conditions (step \circlenum{3}).
The study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks}, which encompasses 797 build logs from
80 popular open-source projects and a broad range of different
build tools and programming languages.
Our results show that there is no technique that in general outperforms
the others.
PBE has the best average precision of 95\%, while KWS has the largest
recall with 70\% on average.
However, CTS shows the best F$_{1}$-score
of 51\% and all of the three techniques
clearly surpass a random baseline.

@@

In short, this article contributes
\begin{itemize}
\item the first systematic survey of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\item systematic guidelines on when to use which technique.
\item a detailed research map to inspire future contributions to the
field.
% (resolved) only point with no adjective
\item a documented replication package~\cite{brandt2020chunk-replication}.
\end{itemize}

@@

We performed a systematic mapping study on the emerging field of
build log analysis,
to determine how various researchers analyze build logs.
We start this section by explaining how build log analysis differs
from the more established field of
system log analysis.
% ref to fig 2 so it can be here and above fig 3
Then, we describe the methodology (\Cref{fig:lit-survey})
and results of our systematic mapping
survey following the
guidelines by Petersen et
al.~\cite{petersen2008systematic,petersen2015guidelines}.
% We close by summarizing how build logs are commonly
% analyzed in literature and discuss the implications of these findings.

@@

When analyzing system log files, the first goal is generally to
separate the constant and variable parts within a log
message~\cite{nagappan2010abstracting,he2017towards}.
Next, the log
messages are clustered into log events, unifying messages with
identical constant parts and varying parameters.
The output is an ordered list of timed events and their corresponding
parameter values~\cite{he2016evaluation}.
This structured log can serve as input to various machine learning and
data mining processes.

Some of the techniques developed to parse system logs can operate
on build logs as well, such as approaches to retrieve the
values of variable parts in a log message, e.g.\, by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.
% This is the easiest example matching here
% amar et al are not in our literature survey
However, almost all of the techniques developed to analyze system logs
leverage their inherent event structure.
Build logs generally lack this structure and thus require different
bespoke approaches.
% if included: this explanation is not understandable.
% It needs to better embedded in the surrounding text
% One example is comparing execution traces to reference
% traces of intended behavior to detect anomalies.
% Amar et
% al.~\cite{amar2019mining} employed a similar approach to detect
% relevant lines in build logs.
% In this article, we focus on extracting a single specified information
% from the build log as a whole with chunk retrieval techniques.
% Chunk
% retrieval techniques are used as a part of log parsing

@@

\Cref{fig:lit-survey} gives an overview of the literature selection
process.
An initial Google Scholar search for variations of ``build log''
returned more than 2.2 million results on the 15th of March 2020, many
of which stem
from unrelated fields such as construction or wood working.
We refined the search criteria to exclude such obvious
non-related fields and to exclude works on system
logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 search results.
% Our replication package documents the full search
% queries~\cite{brandt2020chunk-replication}.
To make handling so many search results feasible, we employed a
three-pass filtering strategy:

@@

Second, we performed a finer filter phase by (1) reading their abstracts,
and (2) downloading the
full text of the works and searching the
full text
for the occurrence of ``log.''
If a work showed traces of
working with build logs, we included it for the next filter phase.
In total, we
were left with 87 works after the second filtering phases.

Third, since we had been careful to include rather than exclude borderline
works, a deeper evaluation excluded another 15 works from the 87
works left after the second filter phase.
Multiple works were extensions of others.
Of these, we only considered the earliest work which reported on
the analyzing of build logs.
This excluded another 11 works.
In sum, we classified 61 works in detail.

\subsection{Literature Classification}
Having trimmed down the set of works by 95\%, we investigated the
remaining ones in-depth.
Our aim is to characterize how researchers work with build logs.

@@

To support the data extraction we created a template which we filled out
for each of the 61 works.
The template contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping survey with a
pilot:
both authors extracted data from the same five works and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 56 works evenly between the two authors
and inspected each works as closely as necessary to fill out the
template
with confidence,
starting from occurrences of ``log'' or ``build'' within the works's
text.

For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.
An example of this is the question ``What is the source of the build
log?'',
where we assigned tags such as ``Travis CI,''
``Industrial,'' ``Google,'' or
``self-built.''
Once we had classified all works, we went into the second phase of
card sorting
(``execution phase''), in which we grouped tags
together and found synonyms.
% the following adds to the example but is maybe unneeded / too much
For instance, in the case of the build log source we grouped
``Travis'' and ``Travis CI'' together and assigned ``Industrial'' to
all works that used build logs provided by a company.
The replication package contains the data extraction template and all
results of this step~\cite{brandt2020chunk-replication}.

@@

In this section, we give a general overview over our paper population.
We then present the results of the analysis phase along RQs 1.1 through
1.3.

@@

In this section, we describe what sort of information the works in
our survey usually retrieved from build logs.
\Cref{fig:litsur_r} depicts these results.

@@

\Cref{fig:litsur:use} shows the reason for the
% TODO: isn't this discussion already?
investigated works to analyze build logs, and the result also explains
the prevalence of classification.
The majority of works (46\%) used the outcome of their build log
analysis to drive further research---and it is science aims to try to
classify and abstract.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other works (10\%) used the gained insights to give feedback to
developers.
For 8\% of the works the retrieved information was the input
to a next automatic onward processing step:
works chose
tests that should be part of a reduced but still effective test
suite~\cite{shi2018evaluating} or filled a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.

@@

The most mentioned technique (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build
logs''~\cite{rahman2018impact}.
For such imprecise statements it was often not clear if they describe
a complex parser (including a tokenizer, lexer, etc.) or refer to a
simpler parsing tool based on regular expressions.
If we saw evidence for the latter, we assigned the tag
``Regular Expression'' instead of the tag ``Parser.''
25\% of the works described the use of regular expressions and 20\%
inspected the logs manually.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with a manual categorization of build logs and selected
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.
Another 8\% of the investigated works
employed machine learning such as natural language
processing or information retrieval techniques.
The rather general tags ``analysis'' and ``scan'' in
\Cref{tab:litsur:techniques}, stem---similar to the imprecise
statements about parsing---from the
words authors used to describe their techniques.
%such as
%``automatically analyzed [the build logs]''.

Only 25\% of the works claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five works employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an updated version of them~\cite{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
and
another two
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao}.

\subsubsection{Which kinds of build logs are subject to
  analysis? (RQ 1.3)}
As the structure of build logs can change greatly depending on the
build tools contributing to it~\cite{staahl2014modeling},
we were interested in which (variety) build tools are
investigate in literature.
\Cref{fig:litsur:log_producer} shows the distribution of
build tools whose logs were analyzed by the works in our survey.
Of the works, 30\% analyzed
Maven~\cite{maven2019website},
16\% analyzed Gradle~\cite{gradle2020website},
and 10\% analyzed Ant build logs~\cite{ant2020website}.

A large fraction of the works analyze build logs
from a small number of build tools.
In most cases, this is because the format of build logs
changes and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.
Sometimes, aspects separate from the build log analysis motivate
the limitation to a specific build tool.
For example, Shi et al.
focussed on Maven
build logs because they also chose the PIT tool~\cite{coles2016pit}
to calculate coverage
and mutation score~\cite{shi2018evaluating}.
PIT is only available as a Maven plugin.
Only 7\% of the proposed techniques claimed to be
build tool-agnostic, while
several described they are covering multiple source build tools.
The majority of works (42\%) analyzed logs produced by a build tool
that no second work investigated.

In 38\% of cases, the works collected build logs from Travis
CI~\cite{travisci2019webpage};
18\% of the works analyzed logs from TravisTorrent; and 8\% included
build logs from industrial projects.
The number of logs analyzed varied greatly between the works
and we were not always able to
extract it confidently.

23 of the works analyzed more than a thousand build logs, while one
investigated up to 122 million logs.
Of the surveyed works, 31\% claim to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which
Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying},
and several other works studied.

@@

% ----- descriptive / general -----
Our literature survey shows that despite its relatively young age
(first mentioned in a paper in 2001, vast majority after
2016), \textbf{build log analysis is an established technique}
in the literature, with 61 works making use of it.

We saw that various researchers analyze build logs, often because the
logs are the only available source for the
information they need for their studies~\cite{ren2018automated,
seo2014programmers,beller2017oops,zampetti2017open,rausch2017empirical}.

% ----- information RQ 1.1 -----
In regards to the information that is targeted, \textbf{most build log
analysis approaches aim to retrieve the reason a build failed} by
targeting ``errors'' or ``failing tests''.
% which is what we also do in LogChunks
\textbf{The majority of approaches retrieves specific chunks of
text from the logs.}

% ----- technique RQ 1.2 -----
\textbf{Most log analysis is automated.} Automated approaches are
necessary as many studies target a large number of builds.
works
that explicitly mention a manual analysis of the logs, mostly
restrict their work to few logs or take a ``representative sample to
make manual analysis feasible''~\cite{zolfagharinia2017not}.
We observed \textbf{very little reuse of build log analysis tools},
even though works reported that
\textbf{developing automated analysis tools requires a lot of effort}.
Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone,'' while other
works pointed to the effort of developing a custom tool.
Regular expressions are known to be tedious to
maintain~\cite{michael2019regexes}.
% not sure if we can state that (no data on this, more 'impression')
In addition, we rarely saw works justifying why they use a certain
technique to analyze build logs as there is a general \textbf{lack of
guidance on when to use which technique}.

% ----- kinds of build logs RQ1.3 -----
Several works noted the variety in log formats for different build
tools, which requires customizing build log techniques for
every supported build tool.
% The following two sentences are passive, however flipped around
% have a different meaning (we want build tool -> study count)
\Cref{fig:litsur:log_producer} shows that only a few distinct
build tools are the target of
many studies and tools (roughly, area A).
The majority of build tools was however only targeted by one
work each (roughly, area B).
From this we follow that the large tail of
\textbf{seldomly-investigated
environments would benefit from the
existence of a more generic solution.}
% In most cases, \textbf{researchers analyze build logs from open
% source projects}, obtained through Travis CI.
% In addition, we saw several works that targeted the logs of only
% one specific software project.

@@

% TODO Moritz: is this okay (here)?
% maybe it's better to add it to Threats to Validity with the heading:
% \texbf{Modifying the Build Process.}
% Moritz: I think best to decided once we read the paper
% top to bottom.
%For now, it seems ok

>>>>

\IEEEPARstart{I}{n}
the past two decades, Continuous Integration (CI) has become a
ubiquitous best practice to streamline the build process of software
projects~\cite{hilton2016usage,beller2017oops,staahl2014modeling}.
Build logs are a textual by-product that these automatic software
builds create.
As a treasure trove of information~\cite{meyer},
build logs contain trace outputs of not only the elementary steps to
``make'' a project---such as retrieving and resolving dependencies and
compiling---but also about ancillary quality assurance steps---such as
testing the software and running automated static analysis tools~\cite{beller2017oops}.
The
contents and format of build logs can vary highly depending on which tools
are involved in the build process, how they are
configured, and as projects and build tools evolve over
time~\cite{staahl2014modeling}.
Typically, though, they are at least a semi-structured and
somewhat stable journal of the commands executed during the build and
their results.

When a build or one of its steps fails, developers typically scavenge
the logs for information related to the source of the error.
This
manual activity is tedious and prone to
errors~\cite{santolucito2018statically}.
As a single build log can be
over 50 megabytes large~\cite{beller2017oops}, finding the small chunk
of information linked to the actual error, is akin to
searching for a needle in a haystack.
The large number of unrelated, but ambiguous
warnings which many build
logs regularly contain further compounds this problem.
In addition to helping
understand and fix build failures, the information richness of build
logs enables a plethora of other applications: with the help of build
logs, we can better understand and categorize CI failures and compile
errors~\cite{islam2017insights,seo2014programmers}, differentiate
testing practices~\cite{orellana2017differences,vassallo2017a-tale},
train classifiers to do ``predictive CI'' on the build or test outcome
and
duration~\cite{ni2017cost,bisong2017built,haghighatkhah2018test,
machalica2019predictive},
or investigate the role of automated static analysis tools (ASATs)
in CI
builds~\cite{zampetti2017open}.

@@

% TODO Caro: I moved it to the intro
% --- please check how it works for you
Retrospectively analyzing the build logs is not the only solution to the problem---an alternate would be to integrate live plugins into the build process
 such as the JUnit
plugin for Jenkins~\cite{jenkins2020junit-plugin} or
Deflaker by Bell et al.~\cite{bell2018deflaker}. 
Their advantage is that they can precisely report the information which
is required.
However, such plugins are not available for all build tools, they are non-trivial to implement one-off solutions, and they
do not enable the analysis of historical builds. When using such a plugin, one has to decide
beforehand which information should be reported, whereas
build log analysis enables us to leverage all information
present in the build logs. Moreover, build log analyis is the more general soltuion. While they serve an important niche, custom plugins do not make build log analysis redundant.

Despite its central role in helping developers and in enabling
novel, onward processing applications,
the process of how to
% TODO
%automatically
% ^ we survey manual as well, though leaving it out includes too much
% systematically twice -- avoid this
analyze build logs has thus far not been systematically
overviewed as a research topic, bringing us to the first
research question:
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What is the state-of-research to analyze build logs?
\end{simplebox}

To answer this question, we start the investigation in this paper---pictured in
\Cref{fig:overview}---with an
extensive literature survey (step \circlenum{1}).
The survey identifies various strategies to
analyze build logs, among which are developing
custom parsers, using regular expressions, doing manual inspections,
searching for keywords, or performing natural language processing.

However, it also identifies that there is currently no guidance on when to use which of these
approaches.
Unfortunately, our survey also shows that
less than half of the 61 works which rely on build log analysis
describe it in sufficient detail and that
the few available implementations are all based on either a custom parser
or regular expressions.
These two approaches are problematic, as their creation
and maintenance is manual and expensive, does not generalize across build
logs from different build tools, and is prone to errors,
as the experience of
TravisTorrent has
shown~\cite{beller2017travistorrent,travistorrentquestions}.
In fact, some even ``strongly discourage'' the creation of such
parsers~\cite{urli2018design}.
In summary, the outcome of our literature survey shows the need for a new
generation of automated techniques to analyze build logs, which are
openly available and documented in detail, together with
guidance on when to use which technique.

To fill this gap, we created three novel, prototypical
implementations to
automatically analyze build logs (step \circlenum{2}).
The ideas behind the implementations are based on promising approaches
adopted from other research fields and existing build log analysis
techniques by retrieving a substring (chunk) from the build log:
\begin{itemize}
	\item \emph{Program Synthesis by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, using \emph{Common Text Similarity (CTS)},
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}.
\end{itemize}

These three approaches have
different strengths and weaknesses.
As a consequence,
in the second research question we ask:

@@

To answer this question
we conduct an empirical study assessing the performance
of these chunk retrieval techniques in
real-world projects under a variety of conditions (step \circlenum{3}).
The study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks}, which encompasses 797 build logs from
80 popular open-source projects and a broad range of different
build tools and programming languages.
Our results show that all of the three techniques
clearly surpass a random baseline, but have different strengths and weaknesses. There is no technique that in general outperforms
the others.
PBE has the best average precision of 95\%, while KWS has the highest
recall with 70\% on average.
However, CTS shows the best F$_{1}$-score
of 51\%.

@@

In short, this article contributes
\begin{itemize}
\item the first systematic survey of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\item systematic guidelines on when to use which technique.
\item a detailed research map to inspire future contributions to the
field.
\item a documented replication package~\cite{brandt2020chunk-replication}.
\end{itemize}

@@

In this section, we report on the state-of-research in the emerging field of build log analysis by means of a systematic mapping study.
We start with a differentiation of build log analysis 
from the older field of
system log analysis.
% ref to fig 2 so it can be here and above fig 3
Then, we describe the methodology (\Cref{fig:lit-survey})
and results of our systematic mapping
survey following the
guidelines by Petersen et
al.~\cite{petersen2008systematic,petersen2015guidelines}.
% We close by summarizing how build logs are commonly
% analyzed in literature and discuss the implications of these findings.

@@

When analyzing system log files, the first goal is generally to
separate the constant and variable parts within a log
message~\cite{nagappan2010abstracting,he2017towards}.  Next, the log
messages are clustered into log events, unifying messages with
identical constant parts and varying parameters.  The output is an
ordered list of timed events and their corresponding parameter
values~\cite{he2016evaluation}.  This structured log can serve as
input to various machine learning and data mining processes. Apart
from a large body of research on system logs, an equally mature amount of commercial-grade and
opensource tooling exists to analyze system logs---such as, for example, Elasticsearch, Logstash and Kiabana (the so-called ELK stack)~\cite{sanjappa2017analysis,bajer2017building}.

Some of the techniques developed to parse system logs can operate
on build logs as well, such as approaches to retrieve the
values of variable parts in a log message, e.g.\, by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.
% This is the easiest example matching here
% amar et al are not in our literature survey
However, the number of
system logs generated mandates that scalability and efficiency play a
much more important role than for build logs.
In addition, almost all of the techniques developed to analyze system logs
leverage their inherent event structure.   Build logs generally lack this
structure and thus require different bespoke approaches.
% if included: this explanation is not understandable.
% It needs to better embedded in the surrounding text
% One example is comparing execution traces to reference
% traces of intended behavior to detect anomalies.
% Amar et
% al.~\cite{amar2019mining} employed a similar approach to detect
% relevant lines in build logs.
% In this article, we focus on extracting a single specified information
% from the build log as a whole with chunk retrieval techniques.
% Chunk
% retrieval techniques are used as a part of log parsing

@@

\Cref{fig:lit-survey} gives an overview of the literature selection
process.
An initial Google Scholar search for ``build log''
returned more than 2.2 million results on the 15th of March 2020, many
of which stem
from unrelated fields such as construction or wood working.
We refined the search criteria to exclude such obvious
non-related fields and to exclude works on system
logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 search results.
% Our replication package documents the full search
% queries~\cite{brandt2020chunk-replication}.
To make handling so many search results feasible, we employed a
three-pass filtering strategy:

@@

Second, we performed a finer filter phase by (1) reading abstracts,
and (2) downloading the
full text of the works and searching it
for the occurrence of the term ``log.''
If a work showed traces of
working with build logs, we passed it onto the final filter phase.
In total, we
were left with 87 works after the second filtering phase.

Third, since we had been careful to include rather than exclude borderline
works, a deeper evaluation excluded another 15 works from the 87
works left after the second filter phase.
Multiple works were extensions of others.
Of these, we only considered the earliest work which reported on
the analyzing of build logs.
This excluded another 11 works.
In sum, we included and classified 61 works in detail.

\subsection{Literature Classification}
Having trimmed down the set of works by 95\%, we investigated the
remaining ones in-depth.
Our aim was to characterize how researchers work with build logs.

@@

To support the data extraction we created a template which we filled out
for each of the 61 works.
The template contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping survey with a
pilot:
both authors extracted data from the same five works and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 56 works evenly between the two authors
and inspected each work as closely as necessary to fill out the
template
with confidence,
starting from occurrences of ``log'' or ``build'' within the full
text of the work.

For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.
An example of this is the question ``What is the source of the build
log?,''
where we assigned tags such as ``Travis CI,''
``Industrial,'' ``Google,'' or
``Self-built.''
Once we had classified all works, we went into the second phase of
card sorting
(``execution phase''), in which we grouped tags
together and found synonyms.
% the following adds to the example but is maybe unneeded / too much
For instance, in the case of the build log source we grouped
``Travis'' and ``Travis CI'' together and assigned ``Industrial'' to
all works that used build logs from a company.
The replication package contains the data extraction template and all
results of this step~\cite{brandt2020chunk-replication}.

@@

In this section, we first give a general overview over our paper population.
We then present the results of the analysis phase along RQs 1.1 through
1.3.

@@

In this section, we describe what sort of information the works in
our survey usually retrieve from build logs.
\Cref{fig:litsur_r} depicts these results.

@@

\Cref{fig:litsur:use} shows the aim for the
% TODO: isn't this discussion already?
% Moritz: Not sure what is meant by that?
investigated works to analyze build logs, and the result also explains
the prevalence of classification in \Cref{fig:litsur:kind}.
The majority of works (46\%) used the outcome of their build log
analysis to drive further research---and it is science's aim to
classify and abstract.
Seo et al.~\cite{seo2014programmers}, for example,
categorized the types of compile errors encountered at
Google.
Other works (10\%) used the gained insights to give feedback to
developers.
For 8\% of the works was the retrieved information the input
to a next automatic onward processing step:
works chose
tests that should be part of a reduced, but still effective test
suite~\cite{shi2018evaluating} or filled     a data structure with
build information, an information source for further tools aiming
to fix a failing build~\cite{vassallo2018un-break}.

@@

The most mentioned technique (34\%) was using a parser. In this tag, we also
included
rather imprecise statements like ``we parse the build
logs''~\cite{rahman2018impact}.
For such imprecise statements it was often not clear if they described
a complex parser (including a tokenizer, lexer, etc.) or refered to a
simpler parsing tool based on regular expressions.
If we saw evidence for the latter, we assigned the tag
``Regular Expression'' instead of the tag ``Parser.''
25\% of the works described the use of regular expressions and 20\%
inspected the logs manually.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with a manual categorization of build logs and selected
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.
Another 8\% of the investigated works
employed machine learning such as natural language
processing or information retrieval techniques.
The rather general tags ``analysis'' and ``scan'' in
\Cref{tab:litsur:techniques}, stem---similar to the imprecise
statements about parsing---from the
words authors used to describe their techniques.
%such as
%``automatically analyzed [the build logs]''.

Only 25\% of the works claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
% TODO The numbers here might look a bit strange
% --- we say five but really it is six works we reference.
% I assume this is because of only including the oldest ref?
% Still, I think we need to fix the inconsistency.
Five works employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an updated version of them~\cite{rott2019empirische,
shi2018evaluating}, two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise},
and
another two
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao}.

\subsubsection{Which kinds of build logs are subject to
  analysis? (RQ 1.3)}
As the structure of build logs can change greatly depending on which
build tools output to it~\cite{staahl2014modeling},
we were interested in which build tools are
investigated in the literature.
\Cref{fig:litsur:log_producer} shows the distribution of
build tools whose logs were analyzed by the works in our survey.
Of the works, 30\% analyzed
Maven~\cite{maven2019website},
16\% analyzed Gradle~\cite{gradle2020website},
and 10\% analyzed Ant build logs~\cite{ant2020website}.

A large fraction of the works analyze build logs
from a small number of build tools.
In most cases, this is because the format of build logs
changes and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.
Sometimes, aspects separate from the build log analysis motivate
the limitation to a specific build tool.
For example, Shi et al.
focussed on Maven
build logs because they also chose the PIT tool~\cite{coles2016pit}
to calculate coverage
and mutation score~\cite{shi2018evaluating}.
PIT is only available as a Maven plugin.
Only 7\% of the proposed techniques claimed to be
build tool-agnostic, while
several described that they cover multiple build tools.
The majority of works (42\%) analyzed logs produced by a build tool
that no second work investigated.

In 38\% of cases, the works collected build logs from Travis
CI~\cite{travisci2019webpage};
18\% of the works analyzed logs from TravisTorrent; and 8\% included
build logs from industrial projects.
The number of logs analyzed varied greatly between the works
and we were not always able to
extract it confidently.
23 of the works analyzed more than a thousand build logs, while one
investigated up to 122 million logs.
Of the surveyed works, 31\% claim to have published their data to
enable further research.
However, we found no clear reuse of build log data sets with the
exception of TravisTorrent~\cite{beller2017travistorrent}, which
Vassallo et al.~\cite{vassallo2017a-tale},
Ghaleb et al.~\cite{ghaleb2019studying},
% TODO  include the several others as references?
and several others have studied.

@@

% ----- descriptive / general -----
Our literature survey shows that despite its relatively young age
(first mentioned in a paper in 2001, vast majority after
2016), \textbf{build log analysis is already an established technique,} with 61 works in different venues making use of it for a variety of purposes.
We saw that various researchers analyze build logs, often because the
logs are the only available source for the
information they need for their studies~\cite{ren2018automated,
seo2014programmers,beller2017oops,zampetti2017open,rausch2017empirical}.

% ----- information RQ 1.1 -----
In regards to the information that is targeted, \textbf{most build log
analysis approaches aim to retrieve the reason a build failed} by
targeting ``errors'' or ``failing tests.''
% which is what we also do in LogChunks
\textbf{The majority of approaches retrieves specific chunks of
text from the logs.} Chunks in some sense are the overarching concept to the almost equally used categorization, as a categorization can usually be deducted from chunks, but not vice versa.

% ----- technique RQ 1.2 -----
\textbf{Most log analysis is automated.} Automated approaches are
necessary because many studies target a large number of builds.
Works
that explicitly mention manual analysis of the logs, mostly
restrict themselves to few logs or take a ``representative sample to
make manual analysis feasible''~\cite{zolfagharinia2017not}.
We observed \textbf{very little reuse of build log analysis tools},
even though works reported that
\textbf{developing automated analysis tools requires a lot of effort}.
Urli et al.~\cite{urli2018design} strongly discouraged from parsing
build logs for information as it is ``too error prone,'' while other
works pointed to the effort of developing a custom tool.
We know from other research lines that regular expressions, the second most popular way to analyze log files (\Cref{tab:litsur:techniques}), are tedious to
maintain~\cite{michael2019regexes}.
In addition, we rarely saw works justifying why they use a certain
technique to analyze build logs as there is a general \textbf{lack of
guidance on when to use which technique.}

% ----- kinds of build logs RQ1.3 -----
Several works noted the variety in log formats for different build
tools, which requires customizing build log techniques for
every supported build tool.
\Cref{fig:litsur:log_producer} shows that there are only a handful of build tools whose build logs more than one study analyzed, mainly in the Java ecosystem (area \circlenum{A}). Many works target a unique build tool that did not appear in any other study (area \circlenum{B}). 
\textbf{seldomly-investigated
environments would benefit from the
existence of a more generic solution.}
% In most cases, \textbf{researchers analyze build logs from open
% source projects}, obtained through Travis CI.
% In addition, we saw several works that targeted the logs of only
% one specific software project.

@@

% TODO Moritz: is this okay (here)?
% maybe it's better to add it to Threats to Validity with the heading:
% \texbf{Modifying the Build Process.}
% Moritz: I think best to decided once we read the paper
% top to bottom.
%For now, it seems ok
% Needs to go Threats or intro
